Reduced growth due to belowground sink limitation is not fully explained by reduced photosynthesis

### 2016-07-20 manuscript/manuscript_pve.Rmd
captions expanded

```{r allometry, fig.width=6, fig.height=7.8, echo=FALSE,  dev="png", dpi=600,eval=includeFigs}
source("master_scripts/allometryplotting.R")
```  
**Figure 1**. Soil volume treatment means &pm; standard error of height growth (a), diameter growth (b), and seedling leaf area estimated from leaf counts (c) measured weekly of *Eucalyptus tereticornis* seedlings across the experiment duration in 2013.

```{r airvars, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600,eval=includeFigs}
source("master_scripts/airvars_plotting.R")
```  
**Figure 2**. Daily maximum and minimum temperature (a), total daily PPFD (b), and daily maximum vapour pressure deficit (c) across the experiment duration in 2013.

```{r allocation, fig.width=6, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE, dev="png", dpi=600,eval=includeFigs}
source("master_scripts/allocation_plotting.R")
```  
**Figure 3**. Soil volume treatment means of biomass partitioning to leaves, stems, and roots at harvest (a), bi-variate relationships between mass allocation to leaves and stems + roots (b) and leaf mass as a function of fine root biomass with &pm; standard error (c). For (b) lines represent standardized major axis fitting of the log-transformed allometric relationships of leaf mass fraction by treatment. For (c) the dashed line is the 1:1 relationship and the solid line represents the significant log-log model fit (*R*^2^ = 0.82) with equation: log(x) = 0.983log(y) - 0.036.

```{r asat, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600,eval=includeFigs}
source("master_scripts/A_stats_plotting.R")
```  
**Figure 4**. Soil volume treatment means &pm; standard error, across all measurement campaigns (n = 6), of light saturated rates of photosynthesis at 25 &deg;C. Different letters represent significant differences between treatments.

```{r A_tncnitro, fig.width=8, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600, eval=includeFigs}
source("master_scripts/Amax_TNC_N_plotting2.R")
```  
**Figure 5**. Photosynthetic capacity, on a leaf mass basis, as a function of accumulation of leaf starch (a) and leaf nitrogen content without TNC (b). Colors represent bins levels (n = 5) of both leaf starch and nitrogen grouped from low to high. Lines represents predictions, for each bin level, from the linear mixed effects model equation of A~mass~ as a function of starch and nitrogen. The marginal *R*^2^ (fixed effects only) was 0.37 and the conditional *R*^2^ (fixed and random effects) was 0.48 for the complete model. The equation for the full model is y = 28.58(N) - 3.31(Starch) - 0.87(N*Starch) - 221.96.

```{r cuefig, fig.width=6, fig.height=6, echo=FALSE, dev="png", dpi=600, eval=includeFigs}
source("master_scripts/cuefig.R")
```  
**Figure 6**. Ratio of final biomass to modelled net leaf C gain of plants growth in different container sizes.

>>>>

```{r allometry, fig.width=6, fig.height=7.8, echo=FALSE,  dev="png", dpi=600,eval=includeFigs}
source("master_scripts/allometryplotting.R")
**Figure 1**. Seedling growth over the duration of the experiment was strongly reduced in containerized seedlings compared to freely rooted seedlings. Height growth (a), diameter growth (b), and seedling leaf area estimated from leaf counts (c) measured weekly on *Eucalyptus tereticornis* seedlings across the experiment duration in 2013. Shown are soil volume treatment means &pm; standard error.
\
```{r airvars, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600,eval=includeFigs}
source("master_scripts/airvars_plotting.R")
**Figure 2**. Environmental drivers over the course of the experiment. Daily maximum and minimum temperature (a), total daily PPFD (b), and daily maximum vapour pressure deficit (c) in 2013. 
\
```{r allocation, fig.width=6, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE, dev="png", dpi=600,eval=includeFigs}
source("master_scripts/allocation_plotting.R")
**Figure 3**. Biomass partitioning at final harvest did not respond strongly to soil volume treatment. (a) Relative partitioning to leaves, stems, and roots at the final harvest, shown as treatment means (standard errors omitted for clarity). (b) Bi-variate relationships between mass partitioning to leaves and stems + roots. Each symbol is a plant. Lines represent standardized major axis fitting of the log-transformed allometric relationships of leaf mass fraction by treatment. (c) Total plant leaf mass as a function of fine root biomass with &pm; standard error. The dashed line is a 1:1 line and the solid line represents the significant log-log model fit (*R*^2^ = 0.82) with equation: log(x) = -0.36 + 0.983 * log(y).
\
```{r asat, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600,eval=includeFigs}
source("master_scripts/A_stats_plotting.R")
**Figure 4**. Light-saturated photosynthesis (A~sat~) was reduced in containerized seedlings compared to freely-rooted seedlings ('Free'). Shown are soil volume treatment means &pm; standard error, across all measurement campaigns (n = 6), of light saturated rates of photosynthesis at 25 &deg;C. Different letters represent significant differences between treatments (p < 0.05).
\
```{r A_tncnitro, fig.width=8, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600, eval=includeFigs}
source("master_scripts/Amax_TNC_N_plotting2.R")
**Figure 5**. Photosynthetic capacity on a leaf mass basis (A~mass~), was correlated to both leaf starch and nitrogen content. (a) A~mass~ was negatively related to leaf starch (shown as percentage of dry mass), in particular for leaves with higher nitrogen content (N~mass~). (b) A~mass~ was positively related to N~mass~ (expressed as N per unit mass after subtracting TNC content). In both panels, each symbol is an individual measurement of A~mass~ (data across all campaigns are shown). Colors represent bins levels (n = 5) of both leaf starch and nitrogen grouped from low to high. Lines represents predictions, for each bin level, from the linear mixed effects model equation of A~mass~ as a function of starch and nitrogen. The marginal *R*^2^ (fixed effects only) was 0.37 and the conditional *R*^2^ (fixed and random effects) was 0.48 for the complete model. The equation for the full model is y = - 221.96 + 28.58(N) - 3.31(Starch) - 0.87(N*Starch).
\
```{r cuefig, fig.width=6, fig.height=6, echo=FALSE, dev="png", dpi=600, eval=includeFigs}
source("master_scripts/cuefig.R")
**Figure 6**. The final biomass attained per unit total photosynthesis over the duration of the experiment. Note the higher ratio for the freely rooted seedlings compared to the containerized seedlings, indicating a higher carbon-use efficiency. Shown are treatment means, as the model scaling instantaneous leaf photosynthesis to total plant photosynthesis was run once for every treatment.
